Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-17 paper/tex/sections/methods.tex
update galaxy schematic nomenclature

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
    \caption{A schematic illustrating how we create a mock Milky Way galaxy. The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, age-metallicity-radius relation, and vertical distribution.
    On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points colour coded by metallicity. The top panel shows a side-on view and the bottom panel shows a face-on view.}
    \label{fig:galaxy_schematic}
\end{figure*}

Our model for the Milky Way accounts for the low-$\alpha$ disc, high-$\alpha$ disc\footnote{Note that $\alpha$ in this case refers to the abundance of $\alpha$ process elements and is not related to the common envelope efficiency $\alpha_{\rm CE}$.} \footnote{The low- and high-$\alpha$ discs are often also referred to as the thin and thick discs. We use the $\alpha$ nomenclature as there is a clear bimodal distribution in the chemical plane, allowing stars to be split between the two components, as opposed to the vertical distribution which simply cannot be fit by a single exponential.} and central bar/bulge. For each of these components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass. \citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-$\alpha$ discs \citep[e.g.,][]{Snaith+2014}.

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
    \caption{A schematic illustrating how we create a mock Milky Way galaxy. The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, age-metallicity-radius relation, and vertical distribution.
    On the right, we show an example instance of the Milky Way with $250000$ binaries shown as points colour coded by metallicity. The top panel shows a side-on view and the bottom panel shows a face-on view.}
    \label{fig:galaxy_schematic}
\end{figure*}

Our model for the Milky Way accounts for the low-$\alpha$\footnote{Note that $\alpha$ in this case refers to the abundance of $\alpha$ process elements and is \textit{not} related to the common envelope efficiency $\alpha_{\rm CE}$.} disc, high-$\alpha$ disc and central bar/bulge. The low- and high-$\alpha$ discs are often also referred to as the thin and thick discs. We use the $\alpha$ nomenclature as there is a clear bimodal distribution in the chemical plane, allowing stars to be easily decomposed into the two disc components, as opposed to the vertical distribution which cannot be fit by a single exponential but is not easy to split into separate components. For each of the three components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass. \citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-$\alpha$ discs \citep[e.g.,][]{Snaith+2014}.
